---
title: "90's Turkish Pop"
author: "Ada Örken"
date: "Spring 2021"
output: 
  flexdashboard::flex_dashboard:
    storyboard: TRUE
    theme: united
---
```{r}
library(spotifyr)
library(tidyverse)
library(plotly)
library(patchwork)
library(compmus)
library(tidymodels)
library(ggdendro)
library(heatmaply)
library(kknn)

get_conf_mat <- function(fit) {
  outcome <- .get_tune_outcome_names(fit)
  fit %>% 
    collect_predictions() %>% 
    conf_mat(truth = outcome, estimate = .pred_class)
}  

get_pr <- function(fit) {
  fit %>% 
    conf_mat_resampled() %>% 
    group_by(Prediction) %>% mutate(precision = Freq / sum(Freq)) %>% 
    group_by(Truth) %>% mutate(recall = Freq / sum(Freq)) %>% 
    ungroup() %>% filter(Prediction == Truth) %>% 
    select(class = Prediction, precision, recall)
} 
```



### **Turkish Pop 101**: A quest of what makes **90's Turkish Pop** special.
 
**What makes 90's Turkish Pop special?**

  My corpus is a selection of Turkish pop songs. It consists of 50 pop songs from 90's and 50 pop songs randomly chosen from a pool of 150 pop songs equally representing 80's, 2000's and 2010's. The aim is to compare 90's Turkish pop to the rest of the corpus. This is an interesting comparison because 90's songs are highly distinguishable by their general sound. A person who is familiar with 90's Turkish pop can easily guess whether a Turkish pop song is from 90's or not. People sometimes say "sounds 90's like" to describe new music which shows that there are common characteristics of this corpus. Another aspect which makes this comparison interesting is the increasing popularity of the 90's Turkish pop songs. These songs are more popular today than they were 20 years ago, although more recent or older songs do not show the same pattern of popularity. For example 80's songs did not regain their popularity 20 years after their release. I would like to understand what makes 90's songs different. 
  
### **Let's Dance!** 90's Turkish Pop is danceable and positive in valence. {data-commentary-width=300}

 
```{r echo = FALSE, message = FALSE }
turkish_pop_eighties<- get_playlist_audio_features("","3COo0d0k5tbgXB35ai0dvh")
turkish_pop_nineties<- get_playlist_audio_features("", "5b9QmdWinj5f47yUtcjuF0")
turkish_pop_twothousands<- get_playlist_audio_features("","4RhazifKLE2G9JzzEU1KcQ")
turkish_pop_twothousandandtens<- get_playlist_audio_features("", "0hRtOMgx3LdkpaJIJ4i2dS")

turkish_pop_rest <-
  bind_rows(
    turkish_pop_eighties %>% mutate(decade = "80s"),
    turkish_pop_twothousands %>% mutate(decade = "2000s"),
    turkish_pop_twothousandandtens %>% mutate(decade = "2010s"),
  )

turkish_pop_rest_50 <- sample_n(turkish_pop_rest, 50)

turkish_pop_all <-
  bind_rows(
   turkish_pop_rest_50 %>% mutate(category = "Rest"),
   turkish_pop_nineties %>% mutate(decade ="90s", category = "Nineties")
  )

turkish_pop_all_by_features <- turkish_pop_all %>%
  select(category,decade, track.name, danceability, energy, key, loudness, mode, speechiness, acousticness, instrumentalness, liveness, valence, tempo) %>%
  mutate(
    mode = ifelse(mode == 0, "Minor", "Major")
  )

turkish_pop_all_by_features$category <- as.factor(turkish_pop_all_by_features$category)
levels(turkish_pop_all_by_features$category) <- c("Nineties (n=50)", "Rest (n=50)")


danceability <- turkish_pop_all_by_features %>%
  ggplot(aes(x = category, y = danceability)) +
  geom_violin() +
  theme_minimal() +
  labs(
    x = "Decade",
    y = "Danceability"
  ) +
   ggtitle("Danceability of 90's Turkish Pop vs Overall Turkish Pop")+
   theme(plot.title = element_text(size = 7))

valence <- turkish_pop_all_by_features %>%
  ggplot(aes(x = category, y = valence)) +
  geom_violin() +
  theme_minimal() +
  labs(
    x = "Decade",
    y = "Valence"
  ) +
  ggtitle("Valence of 90's Turkish Pop vs Overall Turkish Pop")+
   theme(plot.title = element_text(size = 7))


danceability + valence
```


***
  
To discover what makes 90's pop so unique and different, let's compare some features of 90's to the rest of the corpus. Below, you see the distribution of energy, danceability and valence in 90's songs and in the rest of the Turkish pop. 
These graphs give us some hints about why 90's were special.First of all, no wonder 90's pop parties are so popular, those songs were **danceable**! When we compare the danceability distribution of 90's to the rest of the corpus, we see that in the 90's there are no songs at the lower levels and most of the songs are piled up at higher levels of danceability while the rest of the corpus is more equally distributed.     
Second important observation from these graphs is that, 90's songs were more **positive in valence** when compared to the rest of the corpus. Although there were some sad, depressed and angry songs in 90's as well, the distribution is skewed to happy, cheerful and euphoric songs. 

 
 
### What about some interactions? **Danceability** of songs **increase** with the **valence** in the 90's. 


```{r echo = FALSE}

turkish_pop_interaction_graph <- turkish_pop_all_by_features %>%
  ggplot(                    
    aes(
      x = valence,
      y = danceability,
      size = energy,
      colour = mode,
      label= track.name
    )
  ) +
  geom_point(alpha=0.7) +           
  
  facet_wrap(~category) +     
  
  theme_minimal() + 
 scale_color_manual(values = c("Minor" = "#FF7F50", "Major" = "#4B0082")) +
  labs(                       
    x = "Valence",
    y = "Danceability",
    colour = "Mode",
    size= "Energy"
  ) +
  ggtitle("Interaction of Features in 90's Turkish Pop vs Overall Turkish Pop")
  

ggplotly(turkish_pop_interaction_graph)

```
***
  
  In this graph, let's look at some interactions between these features. Move your mouse on the points to learn the song's name and more about it's features.
  This graph shows us an interaction between danceability and valence of 90's songs. More positive songs are more danceable. The same interaction is not observed in the rest of the corpus. A second observation is that there are more major scale songs in the general Turkish pop compared to the 90s. 
   Our first investigation is already giving us clues about why 90's Turkish pop was special and different than the rest of the Turkish pop. Song were more **positive** and more **danceable** in general and as their danceability increased their positive valence also increased.
  
### **Kal Benimle** (Stay With Me): A 90's song that is neither danceable, nor positive, nor energetic.

```{r}
kal_benimle <-
  get_tidy_audio_analysis("179Tal0hUlBUG9lorZxffT") %>%
  select(segments) %>%
  unnest(segments) %>%
  select(start, duration, pitches)

kal_benimle %>%
  mutate(pitches = map(pitches, compmus_normalise, "euclidean")) %>%
  compmus_gather_chroma() %>% 
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = pitch_class,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude") +
  theme_minimal() +
  scale_fill_viridis_c(option="magma")
```

***

Emel Müftüoğlu's *Kal Benimle* from 90's looks like an outlier in terms of danceability, valence and energy; therefore it deserves further investigation. Its chromagram shows prominence of A-sharp and B in the song which is in accordance with the key that this song has been written: D-sharp minor. My google search tells me that a D-sharp minor is associated with feelings such as deep distress, dealing with anxiety and existential terror, dark depression. This emotional interpretation may show us why this song is an outlayer. 90's Turkish Pop is mostly consisted of happy, danceable and energetic songs. 

### Can we characterize a 90's Turkish Pop Song by its **timbral characteristics**? Unfortunatelly not. 

```{r}

pranga_zinciri <-
  get_tidy_audio_analysis("5he9G7I4mwOJ8WHCQpBs0T") %>% # Change URI.
  compmus_align(bars, segments) %>%                     # Change `bars`
  select(bars) %>%                                      #   in all three
  unnest(bars) %>%                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) %>%
  mutate(
    timbre =
      map(segments,
        compmus_summarise, timbre,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )
pranga_zinciri_ceps <-
pranga_zinciri %>%
  compmus_gather_timbre() %>%
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = basis,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude") +
  theme_minimal() +
  scale_fill_viridis_c(option="magma")+
  ggtitle("Cepstogram of 'Pranga Zinciri' by Ajlan & Mine")
 
 saman_alevi <-
  get_tidy_audio_analysis("6EUF3q2wCMTYaVMticz3Jz") %>% # Change URI.
  compmus_align(bars, segments) %>%                     # Change `bars`
  select(bars) %>%                                      #   in all three
  unnest(bars) %>%                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) %>%
  mutate(
    timbre =
      map(segments,
        compmus_summarise, timbre,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )

 saman_alevi_ceps <-
 saman_alevi %>%
  compmus_gather_timbre() %>%
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = basis,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude") +
  theme_minimal() +
  scale_fill_viridis_c(option="magma")+
  ggtitle("Cepstogram of 'Saman Alevi' by Ozon Orhon")
 
 maalesef <-
  get_tidy_audio_analysis("2Bn3E90Aq8yFcRJDpZdzCo") %>% # Change URI.
  compmus_align(bars, segments) %>%                     # Change `bars`
  select(bars) %>%                                      #   in all three
  unnest(bars) %>%                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) %>%
  mutate(
    timbre =
      map(segments,
        compmus_summarise, timbre,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )

 maalesef_ceps<-
 maalesef %>%
  compmus_gather_timbre() %>%
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = basis,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude") +
  theme_minimal() +
  scale_fill_viridis_c(option="magma")+
  ggtitle("Cepstogram of 'Maalesef' by Mansur Ark")
 
 pranga_zinciri_ceps 
 saman_alevi_ceps 
 maalesef_ceps
 
```

***

After looking at an outlayer last week, this week I am comparing three songs from the corpus which look like belonging to center point. These three songs are similar in higher level features such as danceabilitiy and valence. At that level of danceability and valence we see a clustering which may suggest that those levels are representing a typical 90's Turkish song. What about timbres of these songs? Are they also similar? These three cepstograms show us that rather than a strong component 2 there is no commonality between these three songs. Therefore, we may conclude that what makes them similar is not their timbral characteristics. 



### Is there a formula of a **90's Turksih Pop Song's Structure**: Two verses, two choruses, one bridge? Unfortunatelly not. 

```{r}
pranga_zinciri_ssm <-
pranga_zinciri %>%
  compmus_self_similarity(timbre, "cosine") %>% 
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_fixed() +
    theme_minimal() +
  scale_fill_viridis_c(option="magma")+
  ggtitle("Self Similarity Matrix of 'Pranga Zinciri' by Ajlan & Mine") +
  labs(x = "", y = "")

saman_alevi_ssm <-
  saman_alevi %>%
  compmus_self_similarity(timbre, "cosine") %>% 
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_fixed() +
    theme_minimal() +
  scale_fill_viridis_c(option="magma")+
  ggtitle("Self Similarity Matrix of 'Saman Alevi' by Ozon Orhon") +
  labs(x = "", y = "")

maalesef_ssm <-
  maalesef %>%
  compmus_self_similarity(timbre, "cosine") %>% 
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_fixed() +
    theme_minimal() +
  scale_fill_viridis_c(option="magma")+
  ggtitle("Self Similarity Matrix of 'Maalesef' by Mansur Ark") +
  labs(x = "", y = "")

pranga_zinciri_ssm
saman_alevi_ssm
maalesef_ssm

```

***
If it is not timbre, can it be their general structure what makes these songs similar is my next question. Can there be a specific combination of verses, choruses and bridges which would define a 90's pop song? No such pattern is visible in these three song that I chose to represent the corpus. What stands out in *Saman ALevi* by Ozon Orhon is homogeneity, on the other hand what stands out for *Maalesef* by Mansur Ark is two novelty points in the song. *Pranga Zinciri* by Ajlan & Mine has the clearest structure which is not visible in the other songs. These differences makes me conclude that it is also not the structure of the song which charactirizes a 90's Pop Song. 

### Do 90's Turkish Pop songs share a similar **chordical structure**?

```{r}
circshift <- function(v, n) {
  if (n == 0) v else c(tail(v, n), head(v, -n))
}

#      C     C#    D     Eb    E     F     F#    G     Ab    A     Bb    B
major_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    0,    0)
minor_chord <-
  c(   1,    0,    0,    1,    0,    0,    0,    1,    0,    0,    0,    0)
seventh_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    1,    0)

chord_templates <-
  tribble(
    ~name, ~template,
    "Gb:7", circshift(seventh_chord, 6),
    "Gb:maj", circshift(major_chord, 6),
    "Bb:min", circshift(minor_chord, 10),
    "Db:maj", circshift(major_chord, 1),
    "F:min", circshift(minor_chord, 5),
    "Ab:7", circshift(seventh_chord, 8),
    "Ab:maj", circshift(major_chord, 8),
    "C:min", circshift(minor_chord, 0),
    "Eb:7", circshift(seventh_chord, 3),
    "Eb:maj", circshift(major_chord, 3),
    "G:min", circshift(minor_chord, 7),
    "Bb:7", circshift(seventh_chord, 10),
    "Bb:maj", circshift(major_chord, 10),
    "D:min", circshift(minor_chord, 2),
    "F:7", circshift(seventh_chord, 5),
    "F:maj", circshift(major_chord, 5),
    "A:min", circshift(minor_chord, 9),
    "C:7", circshift(seventh_chord, 0),
    "C:maj", circshift(major_chord, 0),
    "E:min", circshift(minor_chord, 4),
    "G:7", circshift(seventh_chord, 7),
    "G:maj", circshift(major_chord, 7),
    "B:min", circshift(minor_chord, 11),
    "D:7", circshift(seventh_chord, 2),
    "D:maj", circshift(major_chord, 2),
    "F#:min", circshift(minor_chord, 6),
    "A:7", circshift(seventh_chord, 9),
    "A:maj", circshift(major_chord, 9),
    "C#:min", circshift(minor_chord, 1),
    "E:7", circshift(seventh_chord, 4),
    "E:maj", circshift(major_chord, 4),
    "G#:min", circshift(minor_chord, 8),
    "B:7", circshift(seventh_chord, 11),
    "B:maj", circshift(major_chord, 11),
    "D#:min", circshift(minor_chord, 3)
  )

pranga_zinciri_chordogram <- get_tidy_audio_analysis("5he9G7I4mwOJ8WHCQpBs0T") %>%
  compmus_align(bars, segments) %>%
  select(bars) %>%
  unnest(bars) %>%
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "mean", norm = "manhattan"
      )
  ) %>% 
  compmus_match_pitch_template(chord_templates, "euclidean", "manhattan") %>%
  ggplot(
    aes(x = start + duration / 2, width = duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(option = "magma") +
  theme_minimal() +
  labs(x = "Time (s)", y = "") +
  ggtitle("Chordogram of 'Pranga Zinciri' by Ajlan & Mine")

saman_alevi_chordogram <- get_tidy_audio_analysis("6EUF3q2wCMTYaVMticz3Jz") %>%
  compmus_align(bars, segments) %>%
  select(bars) %>%
  unnest(bars) %>%
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "mean", norm = "manhattan"
      )
  ) %>% 
  compmus_match_pitch_template(chord_templates, "euclidean", "manhattan") %>%
  ggplot(
    aes(x = start + duration / 2, width = duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(option = "magma") +
  theme_minimal() +
  labs(x = "Time (s)", y = "") +
  ggtitle("Chordogram of 'Saman Alevi' by Ozon Orhon")

maalesef_chordogram <- get_tidy_audio_analysis("2Bn3E90Aq8yFcRJDpZdzCo") %>%
  compmus_align(bars, segments) %>%
  select(bars) %>%
  unnest(bars) %>%
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "mean", norm = "manhattan"
      )
  ) %>% 
  compmus_match_pitch_template(chord_templates, "euclidean", "manhattan") %>%
  ggplot(
    aes(x = start + duration / 2, width = duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(option = "magma") +
  theme_minimal() +
  labs(x = "Time (s)", y = "") +
  ggtitle("Chordogram of 'Maalesef' by Mansur Ark")

pranga_zinciri_chordogram
saman_alevi_chordogram
maalesef_chordogram
```

***

Chordograms of our three representative songs show that at least *Saman Alevi* and *Pranga Zinciri* have similarities in their chordical structure. These two songs are almost 5 years older than *Maalesef* and may be better candidates for representing 90's Turkish Pop corpus. *Maalesef* may be a transition song from 90's to 2000's. 

### **90's Pop Songs** do not like big **novelties**!


```{r}
maalesef <-
  get_tidy_audio_analysis("2Bn3E90Aq8yFcRJDpZdzCo") %>%
  select(segments) %>%
  unnest(segments)

maalesef %>%
  mutate(loudness_max_time = start + loudness_max_time) %>%
  arrange(loudness_max_time) %>%
  mutate(delta_loudness = loudness_max - lag(loudness_max)) %>%
  ggplot(aes(x = loudness_max_time, y = pmax(0, delta_loudness))) +
  geom_line() +
  xlim(0, 100) +
  ylim(0, 30) +
  theme_minimal() +
  labs(x = "Time (s)", y = "Novelty") +
  ggtitle("Novelty-gram of 'Maalesef' by Mansur Ark")


pranga_zinciri <-
  get_tidy_audio_analysis("5he9G7I4mwOJ8WHCQpBs0T") %>%
  select(segments) %>%
  unnest(segments)

pranga_zinciri %>%
  mutate(loudness_max_time = start + loudness_max_time) %>%
  arrange(loudness_max_time) %>%
  mutate(delta_loudness = loudness_max - lag(loudness_max)) %>%
  ggplot(aes(x = loudness_max_time, y = pmax(0, delta_loudness))) +
  geom_line() +
  xlim(0, 100) +
  ylim(0, 30) +
  theme_minimal() +
  labs(x = "Time (s)", y = "Novelty") +
  ggtitle("Novelty-gram of 'Pranga Zinciri' by Ajlan & Mine")

saman_alevi <-
  get_tidy_audio_analysis("6EUF3q2wCMTYaVMticz3Jz") %>%
  select(segments) %>%
  unnest(segments)

saman_alevi %>%
  mutate(loudness_max_time = start + loudness_max_time) %>%
  arrange(loudness_max_time) %>%
  mutate(delta_loudness = loudness_max - lag(loudness_max)) %>%
  ggplot(aes(x = loudness_max_time, y = pmax(0, delta_loudness))) +
  geom_line() +
  xlim(0, 100) +
  ylim(0, 30) +
  theme_minimal() +
  labs(x = "Time (s)", y = "Novelty") +
  ggtitle("Novelty-gram of 'Saman Alevi' by Ozon Orhon")


kal_benimle <-
  get_tidy_audio_analysis("179Tal0hUlBUG9lorZxffT") %>%
  select(segments) %>%
  unnest(segments)

kal_benimle %>%
  mutate(loudness_max_time = start + loudness_max_time) %>%
  arrange(loudness_max_time) %>%
  mutate(delta_loudness = loudness_max - lag(loudness_max)) %>%
  ggplot(aes(x = loudness_max_time, y = pmax(0, delta_loudness))) +
  geom_line() +
  xlim(0, 100) +
  ylim(0, 30) +
  theme_minimal() +
  labs(x = "Time (s)", y = "Novelty") +
  ggtitle("Novelty-gram of 'Kal Benimle' by Emel Müftüoğlu")





```

***

Here, I compare energy-based novelty functions for my three representative songs of 90's Turkish pop music and the one outlayer. My three representative songs: 'Saman Alevi', 'Pranga Zinciri' and 'Maalesef' show similar patterns with smaller spikes. 'On the other hand, 'Kal Benimle' shows a great variation and greater spikes during the first 100 ms of the song. These four graphs make me conclude that a typical 90's pop song has less novelty in it and more stable. There are not big changes in the energy through-out the songs, they are more stable. 

### Do **90's Turkish Pop Songs** have similar **temporal structure**?

```{r}
maalesef <-get_tidy_audio_analysis("2Bn3E90Aq8yFcRJDpZdzCo") 
maalesef_tempogram <-maalesef %>%
  tempogram(window_size = 8, hop_size = 1, cyclic = TRUE) %>%
  ggplot(aes(x = time, y = bpm, fill = power)) +
  geom_raster() +
  scale_fill_viridis_c(guide = "none", option = "magma") +
  labs(x = "Time (s)", y = "Tempo (BPM)") +
  theme_classic() +
  ggtitle("Tempogram of 'Maalesef' by Mansur Ark")
 


pranga_zinciri <-get_tidy_audio_analysis("5he9G7I4mwOJ8WHCQpBs0T") 
pranga_zinciri_tempogram <-pranga_zinciri %>%
  tempogram(window_size = 8, hop_size = 1, cyclic = TRUE) %>%
  ggplot(aes(x = time, y = bpm, fill = power)) +
  geom_raster() +
  scale_fill_viridis_c(guide = "none", option = "magma") +
  labs(x = "Time (s)", y = "Tempo (BPM)") +
  theme_classic() +
  ggtitle("Tempogram of 'Pranga Zinciri' by Ajlan & Mine")
 


saman_alevi <-get_tidy_audio_analysis("6EUF3q2wCMTYaVMticz3Jz") 
saman_alevi_tempogram <- saman_alevi %>%
  tempogram(window_size = 8, hop_size = 1, cyclic = TRUE) %>%
  ggplot(aes(x = time, y = bpm, fill = power)) +
  geom_raster() +
  scale_fill_viridis_c(guide = "none", option = "magma") +
  labs(x = "Time (s)", y = "Tempo (BPM)") +
  theme_classic() +
  ggtitle("Tempogram of 'Saman Alevi' by Ozon Orhon")

maalesef_tempogram
pranga_zinciri_tempogram
saman_alevi_tempogram

```


***

Tempograms of my three representative songs show that their tempi are stable throughout the songs. Energy-based novelty functions showed that 90's Turkish pop songs were mostly stable, these tempograms support this idea on temporal level. 

 
### Can a **robot** classify a **90's pop song** accurately?  

```{r}

turkish_pop_all_separate <- 
  bind_rows(
    turkish_pop_eighties %>% mutate(decade = "80s"),
    turkish_pop_nineties %>% mutate(decade = "90s"), 
    turkish_pop_twothousands %>% mutate(decade = "2000s"),
    turkish_pop_twothousandandtens %>% mutate(decade = "2010s"),
  )

turkish_pop_features <-
  turkish_pop_all_separate %>%  # For your portfolio, change this to the name of your corpus.
  add_audio_analysis() %>% 
  mutate(
    playlist_name = factor(playlist_name),
    segments = map2(segments, key, compmus_c_transpose),
    pitches =
      map(
        segments,
        compmus_summarise, pitches,
        method = "mean", norm = "manhattan"
      ),
    timbre =
      map(
        segments,
        compmus_summarise, timbre,
        method = "mean",
      )
  ) %>%
  mutate(pitches = map(pitches, compmus_normalise, "clr")) %>%
  mutate_at(vars(pitches, timbre), map, bind_rows) %>%
  unnest(cols = c(pitches, timbre))

pop_recipe <-
  recipe(
    playlist_name ~
      danceability +
      energy +
      loudness +
      speechiness +
      acousticness +
      instrumentalness +
      liveness +
      valence +
      tempo +
      duration +
      C + `C#|Db` + D + `D#|Eb` +
      E + `F` + `F#|Gb` + G +
      `G#|Ab` + A + `A#|Bb` + B +
      c01 + c02 + c03 + c04 + c05 + c06 +
      c07 + c08 + c09 + c10 + c11 + c12,
    data = turkish_pop_features,          # Use the same name as the previous block.
  ) %>%
  step_center(all_predictors()) %>%
  step_scale(all_predictors()) %>%      # Converts to z-scores.
  step_range(all_predictors())    # Sets range to [0, 1].

turkish_pop_cv <- turkish_pop_features %>% vfold_cv(5)

knn_model <-
  nearest_neighbor(neighbors = 1) %>%
  set_mode("classification") %>%
  set_engine("kknn")
turkish_pop_knn <-
  workflow() %>%
  add_recipe(pop_recipe) %>%
  add_model(knn_model) %>%
  fit_resamples(
    turkish_pop_cv,
    control = control_resamples(save_pred = TRUE)
  )

turkish_pop_knn %>% get_conf_mat() %>% autoplot(type = "heatmap")


```

***

Taking into account Spotify's track level features, pitch and chroma information, a KNN model was pretty accurate in classifying Turkish 90's pop songs. The recall rates of the model are the highest for 90's song. These findings support my argument that there is something special about 90's Turkish Pop. I mentioned that humans who are familiar with Turkish Pop are usually capable of classifying a 90's song accurately, it turns out that a robot can also do the same! 

### **Outro**: Some final words

My quest of what makes 90's Turkish pop songs special ends here. Throughout this adventure, we discovered that 90's Turkish Pop songs were more danceable and more happy when compared to the rest of the corpus. Historically, this finding makes sense. In the eighties Turkey was dealing with the destruction left from a military coup that happened in the 1980, in the 2000's there was a big economic crisis and 2010's can be characterized by increase of authoritarianism, terrorism and another military coup. Although, 90's had its own share of political and social problems, compared to the other decades, it was a happy period. Therefore, the songs from this decade reflects this atmosphere. 

Chroma, timbre and temporal features were harder to interpret. However, what was nice to see is that when all the features included a KNN model was highly accurate in classifying 90's Turkish Pop Songs. Therefore, although I am not able to define it perfectly what it is, we may conclude that there is something which makes 90's Turkish Pop songs special!

